%-------------------------
% Resume in Latex
% Author : Aryan Gupta
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage[margin=0.75in]{geometry}
\input{glyphtounicode}
% Use the bm package for bold math symbols
\usepackage{bm}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-10pt}\bfseries\Large\raggedright
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4#5} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%---------- HEADING ----------
\begin{center}
  \textbf{\Huge \scshape ARYAN GUPTA} \\ \vspace{3pt} 
  % \textbf{\Huge \scshape \color[rgb]{0.25, 0.41, 0.88} Aryan Gupta} \\ \vspace{3pt} 
  % {\color{blue}GitHub}
  \small
  \faMobile \hspace{.5pt} \href{tel:6023267916}{+1 (602)326-7916}
  $|$
  \faAt \hspace{.5pt} \href{mailto:aryan.gupta.careers@gmail.com}{aryan.gupta.careers@gmail.com}
  $|$
  \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/agupt295}{{\color{blue}Linkedin}}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/agupt295}{{\color{blue}GitHub}}
\end{center}

%----------- EDUCATION -----------
\section{\color[rgb]{0.25, 0.41, 0.88} Education}
\resumeSubHeadingListStart
  \resumeEducationHeading
    {University of Illinois Urbana-Champaign}{Urbana, Illinois}
    {Master of Computer Science}{Aug 2024 -- Dec 2025}{}{}
\resumeSubHeadingListEnd
\vspace{-0.35cm} % Adjust vertical space as needed
\resumeSubHeadingListStart
  \resumeEducationHeading
    {Arizona State University}{Tempe, Arizona}
    {Bachelor of Science in Computer Science}{\textbf{GPA: 3.96/4.00}}{, Aug 2020 -- May 2024}{}
\resumeSubHeadingListEnd

%----------COURSES---------------
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Course-work:}{ Data-Structures \& Algorithms, Database Management, Web Programming, Software Engineering, iOS Development, Distributed Software Analysis, Computer Security.} \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd

%----------- SKILLS -----------
% \section{Technical Skills}
\section{\color[rgb]{0.25, 0.41, 0.88} Technical Skills}
  \resumeSubHeadingListStart
    \small{\item{
      \textbf{Languages:}{ Java, JavaScript, Python, Swift, C/C++, C\#, SQL. } \\ \vspace{3pt}
      \textbf{Full Stack Development:}{ Web Development (React.js, JavaFX, Node.js, ASP.NET), iOS (SwiftUI), PyQt. } \\ \vspace{3pt}
      \textbf{Databases \& Tools:}{ RDBMS (MySQL, PostgreSQL), NoSQL (MongoDB, Firebase), Git, Docker, Postman API.} \\ \vspace{3pt}
      \textbf{Cloud Services:}{ AWS (CloudFormation, EC2, ELB, S3, RDS, Cloud9 IDE).}
    }}
  \resumeSubHeadingListEnd

%----------- EXPERIENCE -----------

% \section{Work Experience}
\section{\color[rgb]{0.25, 0.41, 0.88} Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Arizona State University}{Tempe, Arizona}
      {Undergraduate Academic Success Tutor}{Sept 2023 \textbf{--} May 2024}
        \resumeItemListStart
          \resumeItem{Prepared personalized learning materials on Java: DS Algo, Math: Calculus-I \& Calculus-II and Science based concepts.}
          \resumeItem{Monitored 100+ coding workshops to prepare students for assignments, class projects \& to foster collaborative learning.}
          \resumeItem{Instructed 1000+ students to review introductory \& advanced course concepts and improve students' study strategies.}
        \resumeItemListEnd

    \resumeSubheading
      {Siemens EDA}{Uttar Pradesh, India}
      {Software Development Engineer Intern}{May 2023 \textbf{--} Aug 2023}
        \resumeItemListStart
          \resumeItem{Developed \textbf{PyQt} app, providing users with better data visualization capabilities of 5000+ AXI read/write transactions.}
          \resumeItem{Utilized \textbf{Python} libraries: \textbf{Matplotlib} to create readable graphs, \textbf{NumPy} \& \textbf{SciPy} to perform numerical computations.}
          \resumeItem{Enabled developers to study trends, compare \& save plots efficiently, reducing the analytical time by roughly 33.3\%.}
          \resumeItem{Improved soft skills including Leadership, Time Management, Team Communication and Agile methodologies.}
        \resumeItemListEnd

    % \resumeSubheading
    %   {Appture Technology}{Jaipur, Rajasthan, India- Online}
    %   {Full Stack Software Development Intern}{May 2023 \textbf{--} Aug 2023}
    %     \resumeItemListStart
    %         \resumeItem{Devised a Full Stack JavaScript solution, for Service Providers in Auto Industry, to track the status of all services.}
    %         \resumeItem{Coded React.js for frontend \& connected to PostgreSQL database via Node.js runtime to handle 1K+ customers.}
    %         \resumeItem{Engaged with Product Development Team to consolidate the Web App, achieving 80 higher customer satisfaction.}
    %     \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- PROJECTS -----------
% \section{Projects}
\section{\color[rgb]{0.25, 0.41, 0.88} Projects}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
      {\textbf{ANDBOUNDS (Capstone Project)} $|$ \emph{Git, SwiftUI, Figma} $|$ \emph{\href{https://apps.apple.com/us/app/andbounds/id6446781054?uo=2}{\color{blue}App Store}}}{}
          \resumeItemListStart
            \resumeItem{Worked on \textbf{SwiftUI} to engineer an iOS app for customers with several foot disabilities to order personalized insoles.}
            \resumeItem{Reorganized the front-end architecture of the app on \textbf{Figma}, and integrated new features to enhance user experience \textbf{(UX)}.}
            \resumeItem{Revamped the iOS application from Storyboard to SwiftUI, while addressing the redundant code and features.}
            \resumeItem{Increased proficiency in \textbf{Git Version Control}, Agile \& Scrum techniques and cross-team communication and planning.}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{INVControl} $|$ \emph{Git, SwiftUI, Firebase} $|$ \emph{\href{https://github.com/agupt295/INVControl}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Managed a Full Stack iOS App in \textbf{SwiftUI}, for proprietors, which can help them manage their inventory efficiently.}
            \resumeItem{Structured Use Case, Class Diagram and MVVM architecture of the application to plan the 1st iteration of the project.}
            \resumeItem{Coded SwiftUI for frontend, \textbf{Firebase} as headless CMS to efficiently manage data for 1000+ users.}
            \resumeItem{Worked on \textbf{Git Version Control}, Customer Feedbacks, Project Planning and Time Management.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{ConnectSocial} $|$ \emph{Java, Scene-Builder, JavaFX, MySQL, JDBC API} $|$ \emph{\href{https://github.com/agupt295/ConnectSocial}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Devised a full stack app that let users make friends, tag and post publicly and like \& comment on others' posts.}
            \resumeItem{Led a team of 4 students to build the GUI using \textbf{Scene Builder}, backend using \textbf{Java}, \& database using \textbf{RDBMS}(MySQL).}
            \resumeItem{Engaged in Leadership, Project Planning, Task Delegation, Team Management \& Communication.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{FastOrder} $|$ \emph{ASP.NET, Web Services}}{}
          \resumeItemListStart
            \resumeItem{Deployed a Service-Oriented Web App, using \textbf{ASP.NET}, on Web Server that imitates an E-Commerce Site for 1000+ users.}
            \resumeItem{Executed 3+ ASPX pages, for Users \& Staff, calling Web Services to encrypt data, store cookies, update cart and pay.}
            \resumeItem{Created 5+ \textbf{WCF} \& \textbf{RESTful Services} to manipulate XML files data, eliminating the need of Database by 100\%.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd

% AWARDS and Achievements
% \section{Honors \& Certifications}
\section{\color[rgb]{0.25, 0.41, 0.88} Honors \& Certifications}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
      \textbf{8 x Dean's List: }{Awarded for 8 consecutive semesters for excellent performance, and maintaining a GPA of 3.96 out of 4.0.} \\ \vspace{2pt}
      \textbf{AWS Cloud Practitioner Essentials: }{Completed certification from Coursera verified by AWS.} \\ \vspace{2pt}
      \textbf{IBM DevOps and Software Engineering Professional: }{Currently pursing this certification from Coursera verified by IBM.}
    }}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}